%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Acknowledgments}

\tab

First and foremost, I am deeply indebted to Professor Sujatha Ramdorai for providing me with extraordinary amounts of time and patience (since my first year undergraduate), sharing her seemingly endless bounty of mathematical knowledge, and challenging me with this exciting and multi-faceted problem. I have learned a great deal from our many conversations and feel privileged to have studied under her supervision. I am also very grateful for the funding I have received from NSERC, the department, and Professor Sujatha. 

In addition, I am extremely grateful to Professor Greg Martin for his patience and suffering since my first year undergraduate studies in guiding me through the world of analytic number theory, enabling me to understand the many recent exciting breakthroughs in the field, especially in understanding the notorious Riemann Hypothesis, (and for reminding me that mathematician is a profession, not just a seeker of knowledge) and I want to thank Professor Lior Silberman for enabling me to understand its automorphic version.  I also want to thank Professors Patrick Brosnan and Bruno Kahn on pointing me to the latest advances in the Hodge conjecture, to Professor Tai-Peng Tsai for his inspiring lectures on the latest results on the Navier-Stokes existence and smoothness problem, to Professor Izabella \L aba for her lectures with the latest results on the Kakeya conjecture, to Professor {\'A}kos Mayar on his lectures on the Green-Tao Theorem, to Professor (MORE TO BE ADDED) , and to every faculty member here at UBC whom I have either taken or sat in on a course with, and for PIMS giving me the use of an office as a luxury to do uninterrupted work.

Studying at the Department of Mathematics at UBC has been wonderful with the extremely helpful and friendly department staff, particularly Roseann Kinsey and Marlowe Dickson. Involvement in the graduate student and number theory community has been a great personal and educational experience, punctuated with many deep (non-)mathematical discussions, for which I would like to thank (COLLEAGUES) amongst many others. 

Simply put, I am only here because of my parents, who have been selflessly supportive throughout my life, let alone my education. I dedicate this thesis to them, as their hardships and struggles have always been for my future well-being. 