Missing:
1. S. Skewes: On the difference $\pi(x)-li(x)$ II. Proc. London Math. Soc.(3), 1955
2. E. Phragm\'en: Sur la logarithme int\'gral et la fonction $f(x) de Riemann, \"Ofversugt af Kong. Vetensk. -Akad. F\"o rhandlingar. Stockholm, 48. pp. 599-616
3. J. Pintz: On the remainder term of the prime number formula V, Effective mean value theorems, Studia Sci. Math. Hungar. 15 (1980), 215-223.
4. J. Pintz: On the remainder term of the prime number formula VI, Effective mean value theorems, Studia Sci. Math. Hungar. 15 (1980), 225-230.

OK
5.  Oscillatory properties of M(x) = sigma-n less-than-or-equal-to x-mu(n) II.

6. On the remainder term of the prime number formula IV.: Sign changes of pi(x) Ð li(x)
STUDIA SCIENTIARUM MATHEMATICARUM HUNGARICA 13: pp. 29-42. (1978)


7. On the remainder term of the primer number formula I.: On a problem of Littlewood.
ACTA ARITHMETICA 36: pp. 27-51. (1979)

8.  On the remainder term of the prime number formula III.: Sign changes of pi(x) Ð li(x)
STUDIA SCIENTIARUM MATHEMATICARUM HUNGARICA 12: pp. 345-369. (1977)

Ford and Konyagin, {\it The prime number race and zeros of $L$-functions off the critical line}, 2002 (I have this reprint)

Ford and Konyagin, {\it The prime number race and zeros of $L$-functions off the critical line, II}, 2003 (I have this preprint)

Ford and Konyagin, {\it Chebyshev's conjecture and the prime number race}, 2004 (I have this preprint); see also Cojocaru's Math Review

Myerscough, {\it Application of an accurate remainder term in the calculation of Residue Class Distributions} (I have this preprint)

Limiting distributions of the classical error terms of prime number theory
A Akbary, N Ng, M Shahabi
The Quarterly Journal of Mathematics

Nathan Ng's work in general

Youness Lamzouri's work in general

Snead, Lead changes....